<<<<<<< HEAD
---
title: "Cleaning"
author: "Marziyeh Aghaei"
date: "2024-07-22"
output:
  html_document: 
    code_folding: show
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r,message = FALSE}
# packages
require(tidyverse)
require(fixest)
require(stargazer)
require(haven)
library(usethis)
library(dplyr)
library(foreign)
library(gridExtra)
library(ggplot2)
library(openxlsx)
library(RODBC)
library(openxlsx)
library(gridExtra)
library(cowplot)
library(RColorBrewer)

# clear
rm(list = ls())

# set general data directory
directory_data <- "C:/lfp/data/raw_data/LFS"
directory_data_main <- "C:/lfp/data/raw_data"
```
```{r}
# Load Data
setwd(directory_data)

# create empty dataframes
df_1384_1386_ref <- data.frame()
df_1387_1402_ref <- data.frame()

# Loop through each file, read the data, and assign to a variable
for (i in 1384:1402) {
    file <- paste0("LFS_", i, ".dta")
    data <- read_dta(file)
    data <- data[, order(names(data))]
    
    # if i<87 merge data with df_84_86, else if i>87 merge data with df_87_99
    if (i < 1387) {
      df_1384_1386_ref <- bind_rows(df_1384_1386_ref, data)
    } else {
      if (i < 1396) {
        data <- subset(data, select = -IW15_Yearly)
        names(data)[names(data) == "IW10_Yearly"] <- "IW_Yearly"
      }
      df_1387_1402_ref <- bind_rows(df_1387_1402_ref, data)
    }
}

# remove variable data
rm(data)

setwd(directory_data_main)

province_list <- read.xlsx("province_names.xlsx")

province_list <- province_list %>%
  rename(
    province_code = Code,
    province_name = Name,
  )

```

```{r}
# separate pkey column into 4 columns
df <- df_1387_1402_ref %>%
  select(-F3_D16SHASLIR,-F3_D16SHASLIS,-F3_D16SHHAMRO,-F3_D16SHHAMSA,-F3_D18CHARSHA,-F3_D18DOSHANB,-F3_D18JAM,
         -F3_D18JOMEH,-F3_D18PANSHAN,-F3_D18SESHANB,-F3_D18YEKSHAN,-F3_D18SHANBEH) %>%
  mutate(pkey_copy = pkey) %>%  # Copy the original pkey column
  separate(pkey_copy, into = c("year", "province_code", "urban_rural", "sample_number", "family_number"), sep = c(2, 4, 5, 8)) %>%
  left_join(province_list, by = "province_code")

df <- df[order(df$pkey), ]

df1 <- df %>%
  mutate(year = ifelse(as.integer(year) >= 87, paste0("13", year), paste0("14", year))) %>%
  mutate(time = paste(year, "-", NobatAmargiri)) %>%
  rename(
    gender = F2_D04,
    age = F2_D07,
    citizenship = F2_D08,
    education = F2_D17,
    family_relation = F2_D03,
  ) %>% 
  mutate(gender=if_else(gender==1,"Male","Female")) %>%
  # filter(age>=16 & age<=64, citizenship==1,urban_rural==1) %>%
  mutate(active = if_else(ActivityStatus == 1 | ActivityStatus == 2 , 1, 0)) %>%
  mutate(age_group = case_when(
    age >= 16 & age < 24 ~ "16-23",
    age >= 24 & age < 32 ~ "24-31",
    age >= 32 & age < 40 ~ "32-39",
    age >= 40 & age < 48 ~ "40-47",
    age >= 48 & age < 56 ~ "48-55",
    TRUE ~ "56+"
  )) %>%
  mutate(education_level = case_when(
      education == 11 ~ "literacy",
      education == 71 ~ "literacy",
      education == 21 ~ "high school",
      education == 31 ~ "high school",
      education == 41 ~ "diploma",
      education == 51 ~ "college",
      education == 52 ~ "college",
      education == 53 ~ "graduate level",
      education == 61 ~ "graduate level",
      education == 1 ~ "literacy",
      education == 2 ~ "high School",
      education == 3 ~ "high School",
      education == 4 ~ "diploma",
      education == 5 ~ "college",
      education == 6 ~ "college",
      education == 7 ~ "graduate level",
      education == 8 ~ "graduate level",
      # education_level == 9 ~ "other"
      TRUE ~ "other" # Keep the original value if no match
  ))  %>%
  mutate(education_level=if_else(F2_D16==2,"no literacy",education_level)) %>%
  mutate(
    F3_D15SAL = as.numeric(F3_D15SAL, na.rm = TRUE),
    F3_D37SAL = as.numeric(F3_D37SAL, na.rm = TRUE)
  ) %>%
  mutate(F3_D36_modified=if_else(F3_D36 != 1 | F3_D36 != 4, 0, NA_real_)) %>%
  mutate(employment_history = as.numeric(pmax(F3_D15SAL, F3_D37SAL, F3_D36_modified, na.rm = TRUE))) %>%
   # Define wife and husband and filter early
  mutate(
    wife = if_else(family_relation %in% c(1, 2) & gender == "Female", 1, 0),
    husband = if_else(family_relation %in% c(1, 2) & gender == "Male", 1, 0)
  ) 
```
```{r}
df2 <- df1 %>%
  # Create wife and husband history/education columns
  mutate(
    wife_lfp_history = if_else(wife == 1, employment_history, NA_real_),
    wife_education_level = if_else(wife == 1, education_level, NA_character_),
    husband_lfp_history = if_else(husband == 1, employment_history, NA_real_),
    husband_education_level = if_else(husband == 1, education_level, NA_character_)
  ) %>%
  # Group by pkey and summarize max values to avoid repetitive mutate calls
  group_by(pkey) %>%
  summarize(
    wife_lfp_history = max(wife_lfp_history, na.rm = TRUE),
    husband_lfp_history = max(husband_lfp_history, na.rm = TRUE),
    wife_education_level = max(wife_education_level, na.rm = TRUE),
    husband_education_level = max(husband_education_level, na.rm = TRUE)
  ) %>% ungroup()
```
```{r}
# import data
df_ref <- read_dta("C:/lfp/data/intermediate_data/data_cleaned.dta")
```
```{r}
df_age_parents <- df_ref %>%
  # Create wife and husband history/education columns
  mutate(age=as.numeric(age)) %>%
  mutate(
    wife_age = if_else(wife == 1, age, NA_real_),
    husband_age = if_else(husband == 1, age, NA_real_),
  ) %>%
  # Group by pkey and summarize max values to avoid repetitive mutate calls
  group_by(pkey) %>%
  summarize(
    wife_age = max(wife_age, na.rm = TRUE),
    husband_age = max(husband_age, na.rm = TRUE),
  ) %>% ungroup()
```

```{r}
# df_final <- df1 %>%
  # left_join(df2, by = "pkey") %>% left_join(df_age_parents, by = "pkey") 
```
```{r}
df_final <- df_ref %>%
  left_join(df_age_parents, by = "pkey") 
```

```{r}
write_dta(df_final, path = "C:/lfp/data/intermediate_data/data_cleaned.dta")
```
      #mutate(wife_lfp_history_group = case_when(
      #wife_lfp_history > 0 & wife_lfp_history < 5 ~ "Less than 5 years",
      #wife_lfp_history >= 5 & wife_lfp_history < 10 ~ "5-10 years",
      #wife_lfp_history >= 10 & wife_lfp_history < 20 ~ "10-20 years",
      #wife_lfp_history >= 20 ~ "20+ years",
      #TRUE ~ "Never worked")) %>%
      #mutate(husband_lfp_history_group = case_when(
      #husband_lfp_history > 0 & husband_lfp_history < 5 ~ "Less than 5 years",
      #husband_lfp_history >= 5 & husband_lfp_history < 10 ~ "5-10 years",
      #husband_lfp_history >= 10 & husband_lfp_history < 20 ~ "10-20 years",
      #husband_lfp_history >= 20 ~ "20+ years",
      #TRUE ~ "Never worked")) %>%



>>>>>>> 9de29109d949c2017a28c35f5e1f6c226a76869d
